---
title: "The Link Between Economic Development and Happiness"
author: 
  - Dilek, Melike[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
    Is there a corelation between gdp per capita and happiness of people?
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: 20450586, [https://github.com/MelikeDilek/Final.git](https://github.com/MelikeDilek/Final.git)





# Introduction

What is the situation in the relationship between income and happiness? Have there been any changes over time? If so, what led to these changes? We investigated these questions for countries with different economic, political and cultural characteristics. For the USA, we can say that the correlation between income and happiness has been increasing since 1972, when both income and income inequality increased.
Studies conducted in Japan between 1978 and 2011 do not indicate a correlation between income and happiness, unlike the USA.
Later, a study conducted in 16 European countries shows that the income-happiness correlation started to increase after 1970 and became particularly evident in the years when high GDP per capita and income inequality were high.
We found that the income-happiness correlation decreased after 1997 in Latin American countries, just like income inequality.
In general, we can say this: In the last 50 years, the income-happiness correlation has increased in the USA and many European countries.
The findings show that the income-happiness correlation increases when perceived income inequality increases and decreases when it decreases.
@owidhappinessandlifesatisfaction; @easterlin2009happiness

## Literature Review

In measuring national levels of happiness in 158 countries for the years 2012 to 2014 we depended on people’s own reports of the quality of their lives. We used a scale from 0 to 10, zero representing the worst, and 10 the best life. 
We used the following six variables: – GDP per capita, healthy life expectancy, social support, freedom, generosity and absence of corruption.
The first 10 countries are small or medium sized industrial countries. Seven of these are western European countries. Starting from the 11th to the 20th we see different geographical regions. 
In the top 10 countries, average life evaluation is 7.4 out of 10. In contrast the bottom 10 have the average 3.4. Three points of this 4-point difference were the result of three of the six variables (GDP per capita, social support, and healthy life expectancy). @10.1093/pnasnexus/pgac224

If we examine the reports of happiness around the world at any given moment, we see that countries with a higher average income have higher life satisfaction scores. People in rich countries lead happier lives. This determination is also true over time, because as countries get richer, people's happiness scores increase. Countries where people live longer are also countries where people tend to say that they are satisfied with their lives. This shows the strong correlation between life expectancy and happiness level.
Having a shared history and culture stands out as a factor that increases happiness. For example, the level of happiness in Latin American countries is higher than in other countries in the same economic conditions. Similarly, former communist countries have lower happiness scores than countries with the same level of economic prosperity.
There is a positive correlation between happiness and sense of freedom. Countries where people feel free to choose among options and control their lives to some extent are happier countries.
As an interesting example, although there are a few countries with a high sense of freedom but a low happiness score, such as Rwanda, no country with a low sense of freedom but a high happiness score was found.@CORAZZINI2012715

There are many studies that show that there is a strong correlation between economic welfare and development level and happiness. One of the reasons why the findings are so consistent is that serious unhappiness factors such as inflation and unemployment are effective in countries where economic welfare is not high. @helliwell2015geography



```{r}
```



```{r plot, fig.align='center', fig.cap='An Awesome Plot'}

```


# Conclusion
In order to understand whether happiness is felt with a relative or an absolute perception, the following results were obtained in a study of 3,900 people, four of which were in low-income (Bolivia, Brazil, Kenya and Laos) and four other high-income countries (Italy, Switzerland, Sweden and the UK). It has been found that the perception of happiness is more relative in high-income countries, whereas in low-income countries, the satisfaction of basic needs is a more important issue, so the perception of happiness is more absolute. 
To conclude, bearing in mind the important role played by personal characteristics such as gender and background, we can add that when expressing an opinion on how happy they are, people compare themselves both to those 'above' and 'to those below', and not just their place in the rankings, but the absolute income of the groups they compare themselves to. considering their size. As a result, the perception of happiness is determined by absolute income rather than relative income.@CORAZZINI2012715




\newpage
# References {#references}
<div id="refs"></div>

